exponential Bradley-Terry

### 2025-04-07 inst/exponential_BT.Rmd
lando

>>>>

## Formula 1

```{r checo}
n <- 20 # 20 drivers
multiple_like_fun <- function(n,           # n competitors
                            a_try, x_try,  # values to try
                            N=1e2){        # N is number of trials
    p_try <- ceiling(n * a_try)
    jj <- as.matrix(expand.grid(p_try, x_try))
    t(apply(jj,1,function(v){getprob(n, v[1], v[2], N)}))
}
```

```{r checo2023}
o <- c(6,8,3,5,2,1,2,4,2,2,20,3,2,5,1,3,4,1,4,2,6,6,10) # lando norris 2024
```

```{r trymultx, cache=TRUE}
II <- multiple_like_fun(20, a_try,x_try,1e4)
head(II)
nrow(II)
length(a_try)
length(x_try)
```

```{r calcmultx, cache=TRUE}
like <- list()
dim(II)
o
for(i in seq_along(o)){
    like[[i]] <-  matrix(II[, o[i] + 2], length(a_try), length(x_try))
}
```

```{r showlike}
like
alllike <- Reduce("*",like)
alllike 
alllike/max(alllike)
S <- log(alllike)
S <- S-max(S)
S <- pmax(S,-15)
contour(S,levels = -(0:6)*2, lwd=c(1,4,1,1,1,1,1))
filled.contour(S)
```
